Metabolites reflect variability introduced by mesoscale eddies in the North Pacific Subtropical Gyre

### 2024-10-21 manuscript/manuscript.Rmd
Adding note about blanks and their use

Compounds for which we had an authentic standard (Supplemental Table 2) were manually integrated using Skyline and MSDIAL with the standard mixes used to ensure the correct peak was integrated by matching retention time. Compounds that were visually determined to have poor peak quality in the samples were removed from the downstream analysis. Skyline was used for both the eddy center samples and the HEE cruise data while MSDIAL was used for the eddy transect data due to the larger number of files in that dataset. Raw peak areas were then normalized to their best-matched internal standard (Supplemental Table 1) per @Boysen2018 except that all compounds were normalized to their best match no matter how minimal the improvement. Normalized peaks were then calibrated via a single-point standard curve as determined uniquely for each compound from the authentic standard mixes and used to convert normalized peak area into moles per µL injected and scaled to the amount of seawater filtered to provide a final estimate of environmental concentration for each compound in moles per liter of seawater filtered.

>>>>

Compounds for which we had an authentic standard (Supplemental Table 2) were manually integrated using Skyline and MSDIAL with the standard mixes used to ensure the correct peak was integrated by matching retention time. Compounds were removed from the analysis if they were visually assessed to have poor peak quality in the samples or peak areas in the samples similar to those in the methodological blanks. Skyline was used for both the eddy center samples and the HEE cruise data while MSDIAL was used for the eddy transect data due to the larger number of files in that dataset. Raw peak areas were then normalized to their best-matched internal standard (Supplemental Table 1) per @Boysen2018 except that all compounds were normalized to their best match no matter how minimal the improvement. Normalized peaks were then calibrated via a single-point standard curve as determined uniquely for each compound from the authentic standard mixes and used to convert normalized peak area into moles per µL injected and scaled to the amount of seawater filtered to provide a final estimate of environmental concentration for each compound in moles per liter of seawater filtered.
